---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# packagepal

<!-- badges: start -->
<!-- badges: end -->

The goal of packagepal is to be a good pal for R package builders.

## Installation

You can install the development version of packagepal from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("lddurbin/packagepal")
```

## Get Started

To get started with packagepal, call the following function and follow the instructions:

```{r example, eval=FALSE}
packagepal::pal_start()
```

## Acknowledgements

This package was inspired by Building Tidy Tools, a workshop delivered by Emma Rand and Ian Lyttle at rstudio::conf(2022). Although I didn't attend this workshop myself, the slides are [freely available online](https://rstudio-conf-2022.github.io/build-tidy-tools/) and taught me how to make my first R package. I still refer to them all the time.
