---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# packagepal

<!-- badges: start -->
[![R-CMD-check](https://github.com/lddurbin/packagepal/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/lddurbin/packagepal/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/lddurbin/packagepal/graph/badge.svg)](https://app.codecov.io/gh/lddurbin/packagepal)
<!-- badges: end -->

The goal of packagepal is to be a good pal for R package builders.

## Installation

``` r
install.packages("packagepal")
```

## Get Started

To get started with `packagepal`, simply call:

```{r package_checklist, eval=FALSE}
packagepal::checklist()
```


## Acknowledgements

This package was inspired by Building Tidy Tools, a workshop delivered by Emma Rand and Ian Lyttle at rstudio::conf(2022). Although I didn't attend this workshop myself, the slides are [freely available online](https://rstudio-conf-2022.github.io/build-tidy-tools/) and taught me how to make my first R package. I still refer to them all the time.

I have also borrowed ideas from *R Packages (2e)* by Hadley Wickham and Jennifer Bryan, as well as here: [https://github.com/DavisVaughan/extrachecks](https://github.com/DavisVaughan/extrachecks)
